---
title: "Impact of Education Level on Satisfaction with Federal Government"
author: "Chen,Shupeng"
date: 2020-09-24
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(tidyverse)
library(usethis)
library(devtools)
library(cesR)
```

# Abstract
In capitalist countries, popular satisfaction with the federal government often determines whether it wins elections.In this paper we explore the 2019 CES dataset,which was a non-probability survey**^1^** conducted in the lead-up to the 2019 Federal Election. We found that people''s education level is closely related to their satisfaction with the federal government.Our findings have certain reference value to the governing  party's re-election.



```{r cars}
summary(cars)
fit <- lm(dist ~ speed, data = cars)
```

# Including Plots

You can also embed plots. See Figure \@ref(fig:pie) for example:

```{r pie, fig.cap='A fancy pie chart.', tidy=FALSE}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```
